---
title: "SfL functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SfL functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(SfL)
```

SfL provides small teaching-oriented helpers while leaving model fitting and
specialised inference to established R packages.

## Descriptive helpers

```{r}
mode_stat(c(1, 1, 2, 3))
se(c(1, 2, 3, 4))

data("data_s")
create_error_bar_df(data_s, "sDur", "pauseBin", type = "std")
```

## Correlations

```{r}
corfun(data_s, c("sDur", "sDurLog", "speakingRate"))
```

`correlation_matrix()` creates a base-R pairs plot with correlation
coefficients, histograms, and optional smoothers.

## Mixed-model R-squared

SfL 1.0.0 calculates marginal and conditional R-squared values for Gaussian
`lme4::lmer()` models without requiring MuMIn.

```{r, eval=requireNamespace("lme4", quietly=TRUE)}
model <- lme4::lmer(Reaction ~ Days + (Days | Subject), lme4::sleepstudy)
mixed_model_r2(model)
```

## Workshop resources

Slides and exercises are hosted on GitHub Pages. These examples are not run
while building the vignette because they open a web browser.

```{r, eval=FALSE}
open_slide(3, 2021, "english")
open_exercise(2, 2021, "english")
```

## Optional plotting packages

```{r, eval=FALSE}
install_workshop_packages()
```
